Coding theory package for {\it Macaulay2}

### 2021-05-15 tex/answers.tex
Changed optional argument 'Strategy' of minimumWeight to 'Strat' as a work-around for a bug causing documentation related warnings on installation.
added line about the GPLv3 license

\begin{document}
\begin{center}
Response to reviews
\end{center}
We would like to thank you for your careful reading of our manuscript and for your insightful comments which have served to improve our submission. This document contains an overview of the changes that have been made in response to previous comments.
\\

@@

\item About public domain \textcolor{red}{Gwin, help please}

@@

\item There are no more warnings about missing documentation. \textcolor{red}{Nathan, there is a missing documentation now about the weight function}

>>>>

\begin{document}
\begin{center}
Response to reviews
\end{center}
We would like to thank you for your careful reading of our manuscript and for your insightful comments which have served to improve our submission. This document contains an overview of the changes that we have made.
\\

@@

\item Added a GPLv3 license header. 

@@

\item There are no more warnings about missing documentation.
